---
title: "Final_Project"
author: "Sunday Okechukwu"
date: "2023-04-10"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(corrplot)
```

1. Offer a preliminary description of the data set. For example, indicate the size of the
data source, describe the variables, and include any other data profile information that would be of interest.

## Data Source

[click here view the data source on github](https://github.com/dcgerard/stat_415_615/blob/main/lectures/data/estate.csv)

## Brief Description of the dataset:
 
This dataset is about 522 home sales in a Midwestern city during the year 2002. The goal here is to predict residential home sales prices from the other variables. 

> The 13 variables are described below:

- price: Sales price of residence (in dollars)

- area: Finished area of residence (in square feet)

- bed: Total number of bedrooms in residence

- bath: Total number of bathrooms in residence

- ac: "yes" = presence of air conditioning, "no" = absence of air conditioning

- garage: Number of cars that a garage will hold

- pool: "yes" = presence of a pool, "no" = absence of a pool

- year: Year property was originally constructed

- quality: Index for quality of construction. high, medium, or low.

- style: Categorical variable indicating architectural style

- lot: Lot size (in square feet)

- highway: "yes" = highway adjacent, "no" = highway not adjacent.


# Lets download the data for this project from the Internet

```{r}
# Set the URL of the CSV file to download
url <- "https://dcgerard.github.io/stat_415_615/data/estate.csv"

# Check if a folder named "data" exists in the current working directory
if (!file.exists("data")) {
  # If it doesn't exist, create it
  dir.create("data")
}

# Set the file path for the downloaded CSV file
file_path <- file.path("data", "estate.csv")

# Download the CSV file from the specified URL and save it to the file path
download.file(url, file_path, method = "auto")
```
```{r}
# Read the CSV file into R
estate <- read.csv(file_path)

# View the first few rows of the data to confirm that it was loaded correctly
head(estate)
```
```{r}
# check for null values
# count the number of null values
sum(is.na(estate))
```
```{r}
#Let's drop the id column columns 
estate %>% 
  select(-id) -> estate
```

## Exporing the quantitative variables

```{r}
quant_variables <- estate %>% 
  select(price, area, bed, bath, garage,
        year,style, lot)
quant_variables
```

2. Generate relevant data visual plots that explore multicollinearity for the
quantitative variables and normality for the quantitative variables as well. Also, use
R code to confirm the levels of the categorical variables.

```{r}
# Lets visualize the correlation
corrplot(cor(quant_variables), method = 'number')
```

```{r}
pairs(quant_variables)
```

```{r}
estate2 <- estate %>% 
  select(price, area, quality, style, lot, ac)
estate2
```


```{r}
model <- lm(price ~ area + ac + quality + style + lot , estate2)
model
```

```{r}
summary(model)
```

